---
title: "lab 8"
author: "Drew Andersen"
date: "11/16/2021"
output: html_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(modelsummary)
library(corrplot)
library(broom)
library(here)
library(janitor)
```

```{r}
homes <- read_csv(here("slo_homes.csv")) %>% 
  clean_names()
```

Create a subset for specific cities with summary table
```{r}
home_subset <- homes %>% 
  filter(city %in% c("San Luis Obispo", "Atascadero","Arroyo Grande","Santa Maria-Orcutt"))

home_subset_summary <- home_subset %>% 
  group_by(city, status) %>% 
  summarize(mean = mean(price),
            std = sd(price))
```

```{r}
ggplot(data = home_subset, aes(x = sq_ft, y = price)) +
  geom_point() +
  geom_smooth(method = "lm")
```
Multiple linear regression to investigate relationships between serveral predictor variables and home price.
Two Differrent Models:
(1) price ~ city, bedrooms, bathrooms, sqft, status
(2) price ~ city, sqft, status
(3) try another

```{r}
lm1 <- lm(price ~ city + bedrooms + bathrooms + sq_ft + status, data = home_subset)

lm2 <- lm(price ~ city + sq_ft + status, data = home_subset)

lm3 <- lm(price ~ city + bathrooms + sq_ft, data = home_subset)
```
Use fct_relevel to specify a new reference level

```{r}
homes_quant <- home_subset %>% 
  select(price:sq_ft)

home_cor <- cor(homes_quant)
corrplot(home_cor)
```
Compare AIC values - smaller is better.
Can't determine which is best ----> use both silly :^] 
```{r}
AIC(lm1)

AIC(lm2)
```
Use modelsummary() to return multiple model outputs
```{r}
modelsummary(list(lm1,lm2,lm3))
```
Diagnostic Plots
```{r}
plot(lm1)
```
If coooks distance is greater than 1, then it is pulling more weight than expected of a single point

Use broom::augment() to return the predictions for existing observations
Can follow with a histogram of residuals, rather than a QQ plot
  --> normal distribution is good 
```{r}
home_predictions <- augment(lm1)

ggplot(data = home_predictions) +
  geom_histogram(aes(x=.resid))
```

#BRANCHES are SICK